The need for accuracy and smoothness in numerical simulations

### 2024-05-14 report/src/draft.tex
Typo

In this paper we derive and illustrate the use of Richardson extrapolation using a variety of numerical experiments.
GROMACS is a state-of-the-art library for molecular dynamics that is widely used in academia \cite{gromacs2005}.
We demonstrate that the output of the GROMACS is not always amenable to Richardson extrapolation. 
We identify two conditions that are not always satisfied by GROMACS and we demonstrate that each condition is necessary for the successful application of Richardson extrapolation.
Our data and software is freely available from our GitHub \cite{spockcc2024ppam} repository along with every script and function needed to replicate every number, table and figure from scratch. The names of our MATLAB functions are written with a typewriter font, e.g., \texttt{plot\_shells}.

@@

The authors would like to thank Jesús Alastruey-Benedé, Pablo Ibáñez and Pablo García-Risueño for stimulating discussions on the subject matter.
The first author is supported by eSSENCE, a collaborative e-Science programme funded by the Swedish Research Council within the framework of the strategic research areas designated by the Swedish Government.
This work has been partially supported by the Spanish Ministry of Science and Innovation MCIN/AEI/10.13039/501100011033 (grant PID2022-136454NB-C22), and by Government of Aragon (T58_23R research group).

>>>>

In this paper we derive and illustrate the use of Richardson extrapolation using a variety of numerical experiments.
GROMACS is a state-of-the-art library for molecular dynamics that is widely used in academia \cite{gromacs2005}.
We demonstrate that the output of GROMACS is not always amenable to Richardson extrapolation. 
We identify two conditions that are not always satisfied by GROMACS and we demonstrate that each condition is necessary for the successful application of Richardson extrapolation.
Our data and software is freely available from our GitHub \cite{spockcc2024ppam} repository along with every script and function needed to replicate every number, table and figure from scratch. The names of our MATLAB functions are written with a typewriter font, e.g., \texttt{plot\_shells}.

@@

The authors would like to thank Jesús Alastruey-Benedé, Pablo Ibáñez and Pablo García-Risueño for stimulating discussions on the subject matter.
The first author is supported by eSSENCE, a collaborative e-Science programme funded by the Swedish Research Council within the framework of the strategic research areas designated by the Swedish Government.
This work has been partially supported by the Spanish Ministry of Science and Innovation MCIN/AEI/10.13039/501100011033 (grant PID2022-136454NB-C22), and by Government of Aragon (T58\_23R research group).
